On the Origin of Shrimpoluminescence

### 2021-12-15 sonoluminescence/paper/paper.tex
asdsad

\section{The Rayleigh-Plesset Equation}
Derive the RP equation here

>>>>

\section{The Rayleigh-Plesset Equation}
The Rayleigh-Plesset (RP) equation can be deduced from the compressible Navier-Stokes equations \cite{}. To that end, we first remind the reader of the Navier-Stokes equations.

The \emph{total} change (in time) of mass in an arbitrary element of a fluid (whose coordinates and boundary may depend on time) is given by  $\frac{d}{dt} \int_{\Omega_t} \rho dV$ where $\Omega_t$ is the domain of the fluid element under consdiration and $\rho(\bm{x},t)$ is the local, time-dependent density of the fluid. Using the transport theorem of fluid dynamics \cite{mcdonough2009lectures}, Gauss's theorem, and (with only some loss of generality) taking $\Omega_t$ to be a \emph{fluid parcel} (so that the boundary of the fluid parcel, $\partial \Omega_t$, moves with the fluid's velocity, $\bm{u}(\bm{x},t)$), this becomes
\begin{equation}
    \frac{d}{dt} \int_{\Omega_t} \rho dV = \int_{\Omega_t} \frac{\partial \rho}{\partial t} dV+\int_{\partial \Omega_t} \rho \bm{u} \cdot \bm{n} dA = \int_{\Omega_t} \frac{\partial \rho}{\partial t}+\nabla \cdot(\rho \bm{u})dV.
    \label{eq:mass_continuity}
\end{equation}
Now to have \emph{mass-continuity}, which we will require on physical grounds, we set eq. \ref{eq:mass_continuity} to 0. Basically, we are saying no additional material is being added or removed from the fluid. Since the fluid parcel's boundary $\Omega_t$ is arbitrary, we find that $\frac{\partial \rho}{\partial t}+\nabla\cdot(\rho \bm{u})\equiv 0$ which is true for every point in the fluid volume.

Newton's second law for fluids (\emph{momentum-continuity}) is defined similarly. We write the momentum-density as $\rho \bm{u}$ with momentum given by $\int_{\Omega_t} \rho \bm{u} dV$. To simiplify what follows, we focus on only the $i^{th}$ component of velocity at a time. Then Newton's second law can be written as 
\begin{equation}
    \frac{d}{dt} \int_{\Omega_t} \rho u_i dV =  \int_{\Omega_t} \frac{\partial (\rho u_i)}{\partial t} dV+\int_{\partial \Omega_t} \rho u_i ( \bm{u} \cdot \bm{n}) dA = F_i.
\end{equation}
Now using Gauss's theorem, the product rule, and mass-continuity we find $ \frac{d}{dt} \int_{\Omega_t} \rho u_i dV =  \int_{\Omega_t} \rho \frac{d u_i}{dt} dV = F_i $. In vector notation this reads
\begin{equation}
    \int_{\Omega_t} \rho \frac{d \bm{u}}{dt} = \bm{F}
    \label{eq:mom_continuity}
\end{equation}

Now let us seperate the forces into \emph{body-} and \emph{surface-forces}: $\bm{F}=\int_{\Omega_t} \bm{f}_B dV+ \int_{\partial \Omega_t} \bm{f}_S dA $. If we only consider an ideal fluid, the surface part can be written as $\int_{\partial \Omega_t} \bm{f}_S dA =-\int_{\partial \Omega_t} p \bm{n} dA = -\int_{\Omega_t}\nabla p dV$ with $p$ the pressure  and the minus sign being due to the sign convention: \emph{out} of the surface $\partial \Omega_t$ is positive. If instead the fluid is real, we can't neglect viscous forces. We suppose that viscous surface term can be represented by a tensor, $\bm{\tau}$, such that $\bm{f}_S = -p\bm{n}+\bm{\tau} \cdot \bm{n}$ with diagonal elements of $\bm{\tau}$ the \emph{normal} viscous stresses and the other components being \emph{shear} stresses. Note here that $\bm{\tau} \cdot \bm{n}$ denotes matrix multipication. It is conventional to combine the pressure and viscous stresses into a single entity called the \emph{stress-tensor}. We denote it by $\bm{\sigma}=-p\bm{I}+\bm{\tau}$.

The components of the viscous stress tensor $\bm{\tau}$ can be deduced from Newton's law of viscosity and combined with symmetry of the tensor itself \cite{mcdonough2009lectures}. We quote the results here \footnote{We are assuming an \emph{isotropic} fluid so that the the viscosities $\eta$, $\mu$ are the same in all directions. This is true for water.}:
\begin{align}
    \tau_{ii} & = 2 \eta \frac{\partial u_i}{\partial x_i} \\
    \tau_{ij} & =  \mu \left( \frac{\partial u_i}{\partial x_j}+\frac{\partial u_j}{\partial x_i} \right).
\end{align}

The body-force density, $\bm{f}_B$, is due to forces acting in the bulk of the liquid e.g. gravity, electrostatic forces, etc. and is typically from sources external to the liquid. Then the total force on a fluid element is $\bm{F}=\int_{\Omega_t} \bm{f}_B+\nabla \cdot \bm{\sigma} dV$. We can succinctly summarize the momentum-continuity equation as
\begin{equation}
    \int_{\Omega_t} \rho \frac{d \bm{u}}{dt}-\bm{f}_B-\nabla \cdot \bm{\sigma} dV =0
\end{equation}
which is equivalent to $\frac{d \bm{u}}{dt}=\frac{1}{\rho}\left[ \bm{f}_B+\nabla \cdot \bm{\sigma} \right]$.

We would rather have an equation explicitly involving the velocity field $\bm{u}$. To that end, let us work out the stress term.
